Analysis and results

### 2021-10-20 analysis/01_experimental-design.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

    emergency_criticized = issue1 * gov_rel2,
    emergency_crackdown = issue1 * gov_rel3,

@@

@@

    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,

@@

@@

    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3,
    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,

@@

    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,

@@

    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,

@@

    transp_criticized = transp1 * gov_rel2,
    transp_crackdown = transp1 * gov_rel3,
    nottransp = ifelse(transp1 == 0, 1, 0),
    nottransp_criticized = nottransp * gov_rel2,
    nottransp_crackdown = nottransp * gov_rel3,

@@

    transp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    transp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    transp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    transp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    transp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    transp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_smalldonors_criticized = nottransp * fund1 * gov_rel2,
    nottransp_smalldonors_crackdown = nottransp * fund1 * gov_rel3,
    nottransp_wealthydonors_criticized = nottransp * fund2 * gov_rel2,
    nottransp_wealthydonors_crackdown = nottransp * fund2 * gov_rel3,
    nottransp_govgrants_criticized = nottransp * fund3 * gov_rel2,
    nottransp_govgrants_crackdown = nottransp * fund3 * gov_rel3,

@@

    transp_emergency_criticized = transp1 * issue1 * gov_rel2,
    transp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    transp_environment_criticized = transp1 * issue2 * gov_rel2,
    transp_environment_crackdown = transp1 * issue2 * gov_rel3,
    transp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    transp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    transp_refugees_criticized = transp1 * issue4 * gov_rel2,
    transp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_emergency_criticized = nottransp * issue1 * gov_rel2,
    nottransp_emergency_crackdown = nottransp * issue1 * gov_rel3,
    nottransp_environment_criticized = nottransp * issue2 * gov_rel2,
    nottransp_environment_crackdown = nottransp * issue2 * gov_rel3,
    nottransp_humanrights_criticized = nottransp * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = nottransp * issue3 * gov_rel3,
    nottransp_refugees_criticized = nottransp * issue4 * gov_rel2,
    nottransp_refugees_crackdown = nottransp * issue4 * gov_rel3,

@@

    transp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    transp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    transp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    transp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    transp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    transp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    transp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    transp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = nottransp * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = nottransp * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = nottransp * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = nottransp * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = nottransp * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = nottransp * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = nottransp * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = nottransp * fund1 * issue4 * gov_rel3

@@

  # Drop the design and the nottransp helper variable.
  select(-c(org1:gov_rel3, nottransp))

>>>>

    # emergency_criticized = issue1 * gov_rel2,

@@

    # emergency_crackdown = issue1 * gov_rel3,

@@

    # smalldonors_criticized = fund1 * gov_rel2,

@@

    # smalldonors_crackdown = fund1 * gov_rel3,

@@

    # emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
    emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
    # environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,

@@

    # humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,

@@

    # refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,

@@

    # nottransp_criticized = transp1 * gov_rel2,
    transp_criticized = transp2 * gov_rel2,
    # nottransp_crackdown = transp1 * gov_rel3,
    transp_crackdown = transp2 * gov_rel3,

@@

    # nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
    # nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
    # nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
    # nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
    # nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
    # nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,

@@

    # nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    transp_emergency_criticized = transp2 * issue1 * gov_rel2,
    # nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
    # nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    transp_environment_criticized = transp2 * issue2 * gov_rel2,
    # nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    transp_environment_crackdown = transp2 * issue2 * gov_rel3,
    # nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
    # nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
    # nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    transp_refugees_criticized = transp2 * issue4 * gov_rel2,
    # nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    transp_refugees_crackdown = transp2 * issue4 * gov_rel3,

@@

    # nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
    # nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
    # nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
    # nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
    # nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
    # nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
    # nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
    # nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,
    transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3

@@

  select(-contains("1"))

### 2021-10-20 analysis/02_clean-data.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

# Load the interactions and join to the design.
interactions_design <- dummy_design %>% 
  left_join(
    read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
    select(-`...1`) %>%
    rename(
      version = question_set,
      task = question,
      alt = choice
    )
  )

@@

# Reintroduce org1 and add the outside option coded as all zeros.
for (n in 1:dim(dummy_X)[1]) {
  # Filter for respondent n.
  dummy_X_n <- dummy_design %>% filter(version == data$version[n])
  interactions_X_n <- interactions_design %>% filter(version == data$version[n])
  for (s in 1:dim(dummy_X)[2]) {
    # Filter for task s and include placeholder for org1.
    dummy_X_s <- dummy_X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:gov_rel3)
    interactions_X_s <- interactions_X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:nottransp_smalldonors_refugees_crackdown)
    for (p in 1:(dim(dummy_X)[3]-1)) {
      # Filter for task s and alt p orgs.
      dummy_X_p <- dummy_X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      interactions_X_p <- interactions_X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      # Fill in org1 to complete org intercept.
      dummy_X_s[p, "org1"] <- ifelse(sum(dummy_X_p) == 1, 0, 1)
      interactions_X_s[p, "org1"] <- ifelse(sum(interactions_X_p) == 1, 0, 1)
    }
    # Save modified design, including outside option.
    dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
    interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
  }
}
```

>>>>

# Load the interactions and join to the design.
interactions_design <- read_csv(here::here("data", "derived_data", "interactions.csv")) %>%
  select(-`...1`) %>%
  rename(
    version = question_set,
    task = question,
    alt = choice
  )

@@

# Reintroduce org1 and add the outside option coded as all zeros.
for (n in 1:dim(dummy_X)[1]) {
  # Filter for respondent n.
  dummy_X_n <- dummy_design %>% filter(version == data$version[n])
  interactions_X_n <- interactions_design %>% filter(version == data$version[n])
  for (s in 1:dim(dummy_X)[2]) {
    # Filter for task s and include placeholder for org1.
    dummy_X_s <- dummy_X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:gov_rel3)
    interactions_X_s <- interactions_X_n %>%
      filter(task == s) %>%
      mutate(org1 = 0) %>%
      select(org1, org2:transp_smalldonors_refugees_crackdown)
    for (p in 1:(dim(dummy_X)[3]-1)) {
      # Filter for task s and alt p orgs.
      dummy_X_p <- dummy_X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      interactions_X_p <- interactions_X_n %>%
        filter(task == s, alt == p) %>%
        select(org2:org4) %>%
        as_vector()
      # Fill in org1 to complete org intercept.
      dummy_X_s[p, "org1"] <- ifelse(sum(dummy_X_p) == 1, 0, 1)
      interactions_X_s[p, "org1"] <- ifelse(sum(interactions_X_p) == 1, 0, 1)
    }
    # Save modified design, including outside option.
    dummy_X[n, s,,] <- rbind(dummy_X_s, rep(0, ncol(dummy_X_s))) %>% as.matrix()
    interactions_X[n, s,,] <- rbind(interactions_X_s, rep(0, ncol(interactions_X_s))) %>% as.matrix()
  }
}
```

### 2021-10-20 analysis/03_analysis.Rmd
Added an intercept + interactions model (I know the files are still too big, I'll move them to OSF soon)

@@

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  seed = 42
)
run <- list(data = data, fit = fit)
if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r extract-draws, eval=FALSE}
intercept <- 0                            # Intercept-only
public_affairs <- 1                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```

>>>>

# # ##############################
# X_new <- array(NA, dim = c(dim(X)[1:3], 19)) # 13 + interactions
# for (r in 1:dim(X)[1]) {
#   for (s in 1:dim(X)[2]) {
#     X_new[r,s,,] <- X[r,s,,c(1:13, 42:47)] # 13 + interactions
#   }
# }
# X <- X_new
# # ##############################

@@

# Run the model and save data and model output
fit <- stan(
  file = here::here("src", "stan_files", "hmnl_noncentered.stan"),
  data = data,
  iter = 10000,
  thin = 5,
  init = 0,
  seed = 1234
)
run <- list(data = data, fit = fit)
if (intercept == 1 & interactions == 0) write_rds(run, here::here("analysis", "output", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(run, here::here("analysis", "output", "model_runs", "interactions.rds"))
if (public_affairs == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) write_rds(run, here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) write_rds(run, here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(run, here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(run, here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(run, here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
```

@@

```{r extract-draws, eval=FALSE}
intercept <- 1                            # Intercept-only
interactions <- 1                         # Include interactions with the intercept-only model?
public_affairs <- 0                       # Public affairs
political_ideology <- 0                   # Political ideology
social_views <- 0                         # Social views
charity_voluntarism <- 0                  # Charity and voluntarism
demographics <- 0                         # Demographics
public_political <- 0                     # Public affairs + Political ideology
public_political_social <- 0              # + Social views
public_political_social_charity <- 0      # + Charity and voluntarism
public_political_social_charity_demo <- 0 # + Demographics

# Load and extract data and model output
if (intercept == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "intercept.rds"))
if (intercept == 1 & interactions == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "interactions.rds"))
if (public_affairs == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_affairs.rds"))
if (political_ideology == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "political_ideology.rds"))
if (social_views == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "social_views.rds"))
if (charity_voluntarism == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "charity_voluntarism.rds"))
if (demographics == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "demographics.rds"))
if (public_political == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political.rds"))
if (public_political_social == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social.rds"))
if (public_political_social_charity == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) run <- read_rds(here::here("analysis", "output", "model_runs", "public_political_social_charity_demo.rds"))
data <- run$data
fit <- run$fit

@@

# Save draws
if (intercept == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "intercept.rds"))
if (intercept == 1 & interactions == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "interactions.rds"))
if (public_affairs == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_affairs.rds"))
if (political_ideology == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "political_ideology.rds"))
if (social_views == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "social_views.rds"))
if (charity_voluntarism == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "charity_voluntarism.rds"))
if (demographics == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "demographics.rds"))
if (public_political == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political.rds"))
if (public_political_social == 1)  write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social.rds"))
if (public_political_social_charity == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity.rds"))
if (public_political_social_charity_demo == 1) write_rds(draws, here::here("analysis", "output", "posterior_draws", "public_political_social_charity_demo.rds"))
```
